Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an Empirical Study of Strategies in the Moran process for the Iterated Prisoner's Dilemma

### 2018-10-12 main.tex
Relabel supporting information and separate tables

The top 16 strategies are given in Table~\ref{tbl:top_invade}. A variety of
figures showing the performance of all strategies is available in the
appendix.

\begin{table}[!hbtp]
    \centering
    \tiny
    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=3\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top invaders for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_invade}
\end{table}

@@

Table~\ref{tbl:top_resist} shows the top strategies when ranked
according to \(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results
for all strategies are available in the supplementary materials.
Once again none of the short memory strategies previously discussed perform well
for high \(N\).

\begin{table}[!hbtp]
    \tiny
    \centering
    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
            2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
            3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
            4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
            5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
            6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
            7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
            8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
            9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
            10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
            11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
            12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
            13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
            14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
            15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
            16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=3\)}
    \end{subfigure}%

    \begin{subfigure}[t]{\columnwidth}
        \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
            \bottomrule
            \end{tabular}
        \caption{\(N=7\)}
    \end{subfigure}

    \begin{subfigure}[t]{\columnwidth}
        \centering
        \begin{tabular}{llrrrrrrr}
        \toprule
        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
        \midrule
        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
        \bottomrule
        \end{tabular}
        \caption{\(N=14\)}
    \end{subfigure}
    \caption{Top resistors for \(N\in\{3, 7, 14\}\)}
    \label{tbl:top_resist}
\end{table}

@@

\section{Appendix A: List of players}\label{app:list_of_players}

@@

\section{Appendix B: Supplementary figures}

\begin{itemize}
    \item Figures~\ref{invasion-3}-\ref{invasion-14} show the fixation probability \(x_1\)
for each strategy. The mean and error bars are shown against the collection of
all opponents.

    \item Figures~\ref{resistance-3}-\ref{resistance-14} show the fixation probability
\(x_{N-1}\) for each strategy. Again, the mean and error bars are shown against
the collection of all opponents.

    \item Figures~\ref{fig:ranks_v_size_invade}-\ref{fig:ranks_v_size_coexist} show the
ranks of each strategy according to mean absorption probability across all
population sizes.
\end{itemize}

\begin{figure}[!hbtp]
    \centering
    %\includegraphics[ width=\textwidth]{./Fig12.eps}
    \caption{The fixation probabilities \(x_1\) for \(N=3\)}
    \label{invasion-3}
\end{figure}

>>>>

The top 16 strategies are given in
Tables~\ref{tbl:top_invade_3},\ref{tbl:top_invade_7} and
\ref{tbl:top_invade_14}. A variety of figures showing the performance of all
strategies is available in the supporting information.

\begin{table}[!hbtp]
    \centering
    \tiny
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &                       CS &  0.261 &  0.2620 &  0.4478 &   0.403 &  0.8105 &  0.908 &  0.1998 \\
            2  &                  Grudger &  0.259 &  0.2641 &  0.4313 &   0.338 &  0.8097 &  0.908 &  0.1699 \\
            3  &                     MEM2 &  0.258 &  0.2875 &  0.4278 &   0.338 &  0.7977 &  0.907 &  0.1636 \\
            4  &                      \textbf{TF3} &  0.248 &  0.2610 &  0.4267 &   0.338 &  0.7904 &  0.904 &  0.1624 \\
            5  &                 Prober 4 &  0.221 &  0.2400 &  0.4242 &   0.365 &  0.7723 &  0.891 &  0.1755 \\
            6  &             Fool Me Once &  0.257 &  0.2645 &  0.4242 &   0.338 &  0.7938 &  0.904 &  0.1620 \\
            7  &                    Davis &  0.234 &  0.2581 &  0.4218 &   0.338 &  0.7759 &  0.891 &  0.1590 \\
            8  &                 Predator &  0.173 &  0.2590 &  0.4210 &   0.374 &  0.7845 &  0.907 &  0.1824 \\
            9  &            Evolved ANN 5 &  0.255 &  0.3163 &  0.4163 &   0.338 &  0.7872 &  0.879 &  0.1530 \\
            10 &              Evolved ANN &  0.253 &  0.2789 &  0.4163 &   0.338 &  0.7938 &  0.906 &  0.1572 \\
            11 &           Evolved FSM 16 &  0.041 &  0.1391 &  0.4154 &   0.338 &  0.7977 &  0.907 &  0.1830 \\
            12 &              Meta Hunter &  0.123 &  0.2541 &  0.4140 &   0.338 &  0.7807 &  0.892 &  0.1614 \\
            13 &                      \textbf{TF1} &  0.257 &  0.2580 &  0.4139 &   0.398 &  0.7411 &  0.900 &  0.1529 \\
            14 &        PSO Gambler 2\_2\_2 &  0.073 &  0.2643 &  0.4134 &   0.338 &  0.7938 &  0.904 &  0.1727 \\
            15 &     EvolvedLookerUp1\_1\_1 &  0.258 &  0.3004 &  0.4113 &   0.338 &  0.7515 &  0.830 &  0.1369 \\
            16 &  Evolved FSM 16 Noise 05 &  0.247 &  0.3238 &  0.4107 &   0.338 &  0.7977 &  0.906 &  0.1540 \\
            \bottomrule
            \end{tabular}
    \caption{Top invaders for \(N=3\)}
    \label{tbl:top_invade_3}
\end{table}

\begin{table}[!hbtp]
    \centering
    \tiny
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.001 &  0.0313 &  0.2523 &   0.142 &  0.6389 &  0.826 &  0.1931 \\
            2  &        PSO Gambler 2\_2\_2 &  0.004 &  0.0588 &  0.2467 &   0.142 &  0.6096 &  0.826 &  0.1809 \\
            3  &             Fool Me Once &  0.044 &  0.0470 &  0.2459 &   0.142 &  0.6105 &  0.826 &  0.1792 \\
            4  &            Evolved ANN 5 &  0.044 &  0.1092 &  0.2450 &   0.142 &  0.6010 &  0.812 &  0.1722 \\
            5  &              Evolved ANN &  0.042 &  0.0615 &  0.2449 &   0.142 &  0.6104 &  0.826 &  0.1785 \\
            6  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0618 &  0.2443 &   0.142 &  0.6380 &  0.824 &  0.1822 \\
            7  &                  Grudger &  0.044 &  0.0451 &  0.2442 &   0.142 &  0.6420 &  0.826 &  0.1830 \\
            8  &                     MEM2 &  0.044 &  0.0583 &  0.2436 &   0.142 &  0.6143 &  0.826 &  0.1760 \\
            9  &                      \textbf{TF3} &  0.044 &  0.0450 &  0.2430 &   0.142 &  0.6344 &  0.826 &  0.1779 \\
            10 &        PSO Gambler 1\_1\_1 &  0.021 &  0.1033 &  0.2404 &   0.142 &  0.6381 &  0.824 &  0.1710 \\
            11 &                       CS &  0.045 &  0.0450 &  0.2395 &   0.148 &  0.6385 &  0.826 &  0.2169 \\
            12 &  Evolved FSM 16 Noise 05 &  0.044 &  0.1298 &  0.2394 &   0.142 &  0.6143 &  0.826 &  0.1732 \\
            13 &            Evolved HMM 5 &  0.010 &  0.0611 &  0.2390 &   0.142 &  0.6115 &  0.826 &  0.1785 \\
            14 &              Meta Hunter &  0.015 &  0.0465 &  0.2385 &   0.142 &  0.5993 &  0.820 &  0.1751 \\
            15 &                    Davis &  0.036 &  0.0465 &  0.2379 &   0.142 &  0.5953 &  0.820 &  0.1732 \\
            16 &         PSO Gambler Mem1 &  0.018 &  0.1105 &  0.2348 &   0.142 &  0.6370 &  0.825 &  0.1671 \\
            \bottomrule
            \end{tabular}
    \caption{Top invaders for \(N=7\)}
    \label{tbl:top_invade_7}
\end{table}

\begin{table}[!hbtp]
    \centering
    \tiny
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &                   Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           Evolved FSM 16 &  0.000 &  0.0054 &  0.2096 &   0.079 &  0.7241 &  0.842 &  0.2172 \\
            2  &        PSO Gambler 2\_2\_2 &  0.000 &  0.0113 &  0.2042 &   0.079 &  0.5940 &  0.842 &  0.2045 \\
            3  &     EvolvedLookerUp2\_2\_2 &  0.000 &  0.0270 &  0.2014 &   0.079 &  0.6608 &  0.840 &  0.2097 \\
            4  &              Evolved ANN &  0.002 &  0.0164 &  0.2014 &   0.079 &  0.5939 &  0.842 &  0.2074 \\
            5  &            Evolved ANN 5 &  0.002 &  0.0505 &  0.2004 &   0.079 &  0.5940 &  0.834 &  0.2009 \\
            6  &            Evolved HMM 5 &  0.000 &  0.0321 &  0.1972 &   0.079 &  0.5940 &  0.842 &  0.2034 \\
            7  &        PSO Gambler 1\_1\_1 &  0.001 &  0.0455 &  0.1955 &   0.079 &  0.6150 &  0.841 &  0.1931 \\
            8  &             Fool Me Once &  0.002 &  0.0058 &  0.1955 &   0.079 &  0.5940 &  0.842 &  0.2032 \\
            9  &  Evolved FSM 16 Noise 05 &  0.003 &  0.0607 &  0.1943 &   0.079 &  0.5930 &  0.842 &  0.2005 \\
            10 &         PSO Gambler Mem1 &  0.000 &  0.0517 &  0.1920 &   0.079 &  0.6118 &  0.841 &  0.1907 \\
            11 &            Evolved FSM 4 &  0.000 &  0.0000 &  0.1918 &   0.079 &  0.5930 &  0.842 &  0.2049 \\
            12 &              Meta Hunter &  0.000 &  0.0049 &  0.1869 &   0.079 &  0.5883 &  0.840 &  0.1882 \\
            13 &   Evolved ANN 5 Noise 05 &  0.001 &  0.0303 &  0.1858 &   0.079 &  0.5930 &  0.840 &  0.1968 \\
            14 &                Omega TFT &  0.003 &  0.0704 &  0.1849 &   0.079 &  0.5939 &  0.840 &  0.1927 \\
            15 &                Fortress4 &  0.000 &  0.0000 &  0.1848 &   0.066 &  0.5919 &  0.840 &  0.2211 \\
            16 &                      \textbf{TF3} &  0.002 &  0.0041 &  0.1846 &   0.079 &  0.6190 &  0.842 &  0.1890 \\
            \bottomrule
            \end{tabular}
    \caption{Top invaders for \(N=14\)}
    \label{tbl:top_invade_14}
\end{table}

@@

Tables~\ref{tbl:top_resist_3},~\ref{tbl:top_resist_7} and
\ref{tbl:top_resist_14} show the top strategies when ranked according to
\(x_{N-1}\) for \(N\in\{3, 7, 14\}\) and figures showing results for all
strategies are available in the supplementary materials.  Once again none of the
short memory strategies previously discussed perform well for high \(N\).

\begin{table}[!hbtp]
    \tiny
    \centering
        \begin{tabular}{llrrrrrrr}
        \toprule
        {} &                Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
        \midrule
        1  &                    CS &  0.662 &  0.7410 &  0.8359 &   0.796 &  0.9980 &  1.000 &  0.0981 \\
        2  &              Predator &  0.530 &  0.7363 &  0.8121 &   0.789 &  0.9980 &  1.000 &  0.0983 \\
        3  &                   \textbf{TF1} &  0.648 &  0.7330 &  0.8087 &   0.791 &  0.9745 &  0.999 &  0.0775 \\
        4  &             Handshake &  0.225 &  0.6322 &  0.8014 &   0.779 &  0.9980 &  1.000 &  0.1293 \\
        5  &                   \textbf{TF2} &  0.572 &  0.7363 &  0.7957 &   0.790 &  0.9330 &  0.961 &  0.0672 \\
        6  &              Prober 4 &  0.646 &  0.6610 &  0.7905 &   0.750 &  0.9890 &  0.996 &  0.1070 \\
        7  &               Grudger &  0.662 &  0.6620 &  0.7612 &   0.662 &  0.9980 &  1.000 &  0.1224 \\
        8  &           Hard Prober &  0.661 &  0.6620 &  0.7582 &   0.732 &  0.9980 &  0.999 &  0.1079 \\
        9  &                   \textbf{TF3} &  0.594 &  0.6620 &  0.7570 &   0.662 &  0.9969 &  0.999 &  0.1197 \\
        10 &                  MEM2 &  0.662 &  0.6620 &  0.7554 &   0.662 &  0.9980 &  1.000 &  0.1210 \\
        11 &                 Davis &  0.662 &  0.6620 &  0.7536 &   0.662 &  0.9848 &  0.996 &  0.1164 \\
        12 &              Winner21 &  0.662 &  0.6630 &  0.7529 &   0.742 &  0.9218 &  0.948 &  0.0741 \\
        13 &          Fool Me Once &  0.661 &  0.6620 &  0.7489 &   0.662 &  0.9970 &  0.999 &  0.1191 \\
        14 &             Fortress4 &  0.552 &  0.5520 &  0.7467 &   0.707 &  1.0000 &  1.000 &  0.1676 \\
        15 &           Retaliate 3 &  0.662 &  0.6620 &  0.7448 &   0.662 &  0.9538 &  0.986 &  0.1032 \\
        16 &  EvolvedLookerUp1\_1\_1 &  0.662 &  0.6620 &  0.7422 &   0.662 &  0.9792 &  0.998 &  0.1062 \\
        \bottomrule
        \end{tabular}
        \caption{Top resistors for \(N=3\)}
    \label{tbl:top_resist_3}
\end{table}

\begin{table}[!hbtp]
    \tiny
    \centering
            \begin{tabular}{llrrrrrrr}
            \toprule
            {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &    Max &     Std \\
            \midrule
            1  &           CS &  0.858 &  0.9560 &  0.9765 &   0.981 &   1.000 &  1.000 &  0.0203 \\
            2  &          \textbf{TF1} &  0.866 &  0.9521 &  0.9714 &   0.979 &   1.000 &  1.000 &  0.0207 \\
            3  &          \textbf{TF2} &  0.840 &  0.9423 &  0.9677 &   0.976 &   0.998 &  1.000 &  0.0239 \\
            4  &     Predator &  0.741 &  0.9478 &  0.9677 &   0.970 &   1.000 &  1.000 &  0.0367 \\
            5  &    Handshake &  0.448 &  0.8261 &  0.9547 &   0.970 &   1.000 &  1.000 &  0.0848 \\
            6  &     Prober 4 &  0.837 &  0.8500 &  0.9540 &   0.955 &   1.000 &  1.000 &  0.0416 \\
            7  &     Winner21 &  0.858 &  0.8600 &  0.9392 &   0.956 &   0.996 &  0.999 &  0.0486 \\
            8  &  Hard Prober &  0.856 &  0.8560 &  0.9331 &   0.953 &   1.000 &  1.000 &  0.0521 \\
            9  &    Fortress4 &  0.829 &  0.8290 &  0.9255 &   0.925 &   1.000 &  1.000 &  0.0653 \\
            10 &      Grudger &  0.858 &  0.8580 &  0.9198 &   0.858 &   1.000 &  1.000 &  0.0642 \\
            11 &          \textbf{TF3} &  0.858 &  0.8580 &  0.9189 &   0.858 &   1.000 &  1.000 &  0.0638 \\
            12 &        Davis &  0.858 &  0.8580 &  0.9186 &   0.858 &   1.000 &  1.000 &  0.0633 \\
            13 &       Ripoff &  0.856 &  0.8560 &  0.9183 &   0.922 &   0.986 &  0.988 &  0.0484 \\
            14 &       Tester &  0.856 &  0.8560 &  0.9176 &   0.921 &   0.986 &  0.988 &  0.0486 \\
            15 &         MEM2 &  0.858 &  0.8580 &  0.9165 &   0.858 &   1.000 &  1.000 &  0.0636 \\
            16 &  Retaliate 3 &  0.858 &  0.8580 &  0.9161 &   0.858 &   0.999 &  1.000 &  0.0619 \\
            \bottomrule
            \end{tabular}
    \caption{Top resistors for \(N=7\)}
    \label{tbl:top_resist_7}
\end{table}

\begin{table}[!hbtp]
    \tiny
    \centering
        \begin{tabular}{llrrrrrrr}
        \toprule
        {} &       Player &    Min &   5th \% &    Mean &  Median &  95th \% &  Max &     Std \\
        \midrule
        1  &           CS &  0.921 &  0.9970 &  0.9984 &   1.000 &     1.0 &  1.0 &  0.0062 \\
        2  &          \textbf{TF1} &  0.938 &  0.9950 &  0.9973 &   0.999 &     1.0 &  1.0 &  0.0069 \\
        3  &          \textbf{TF2} &  0.925 &  0.9820 &  0.9949 &   0.996 &     1.0 &  1.0 &  0.0104 \\
        4  &     Predator &  0.836 &  0.9912 &  0.9941 &   0.999 &     1.0 &  1.0 &  0.0212 \\
        5  &     Prober 4 &  0.895 &  0.9110 &  0.9863 &   0.996 &     1.0 &  1.0 &  0.0250 \\
        6  &    Handshake &  0.514 &  0.9131 &  0.9812 &   0.999 &     1.0 &  1.0 &  0.0743 \\
        7  &     Winner21 &  0.921 &  0.9210 &  0.9778 &   0.996 &     1.0 &  1.0 &  0.0310 \\
        8  &  Hard Prober &  0.916 &  0.9160 &  0.9731 &   0.995 &     1.0 &  1.0 &  0.0327 \\
        9  &    Fortress4 &  0.929 &  0.9290 &  0.9726 &   0.981 &     1.0 &  1.0 &  0.0287 \\
        10 &       Ripoff &  0.919 &  0.9190 &  0.9669 &   0.978 &     1.0 &  1.0 &  0.0318 \\
        11 &       Tester &  0.919 &  0.9190 &  0.9662 &   0.977 &     1.0 &  1.0 &  0.0320 \\
        12 &      Grudger &  0.921 &  0.9210 &  0.9592 &   0.921 &     1.0 &  1.0 &  0.0390 \\
        13 &          \textbf{TF3} &  0.921 &  0.9210 &  0.9589 &   0.921 &     1.0 &  1.0 &  0.0388 \\
        14 &        Davis &  0.921 &  0.9210 &  0.9588 &   0.921 &     1.0 &  1.0 &  0.0387 \\
        15 &  Retaliate 3 &  0.921 &  0.9210 &  0.9580 &   0.921 &     1.0 &  1.0 &  0.0383 \\
        16 &    Retaliate &  0.921 &  0.9210 &  0.9576 &   0.921 &     1.0 &  1.0 &  0.0382 \\
        \bottomrule
        \end{tabular}
    \caption{Top resistors for \(N=14\)}
    \label{tbl:top_resist_14}
\end{table}

@@

\section*{Appendix: List of players}\label{app:list_of_players}

@@

\section*{Supporting information}

\begin{figure}[!hbtp]
    %\includegraphics[ width=\textwidth]{./S1_Fig.eps}
    \textbf{S1 Fig.} The fixation probabilities \(x_1\) for \(N=3\)
\end{figure}

\begin{figure}[!hbtp]
    %\includegraphics[ width=\textwidth]{./S2_Fig.eps}
    \textbf{S2 Fig.} The fixation probabilities \(x_1\) for \(N=4\)
\end{figure}

\begin{figure}[!hbtp]
    %\includegraphics[ width=\textwidth]{./S3_Fig.eps}
    \textbf{S3 Fig.} The fixation probabilities \(x_1\) for \(N=5\)
\end{figure}

\begin{figure}[!hbtp]
    %\includegraphics[ width=\textwidth]{./S4_Fig.eps}
    \textbf{S4 Fig.} The fixation probabilities \(x_1\) for \(N=6\)
\end{figure}
